\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2018-04-05 write_up/mixfishsim_ecolmod.tex
Responses to JM and JJP comments

\usepackage{lineno,hyperref}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,chains,calc}

@@

\address[1]{Galway-Mayo Institute of Technology (GMIT), Dublin Road, Galway,
	Ireland} 
\address[2]{Centre for Environment, Fisheries and Aquaculture Science (Cefas),
	Pakefield Road, Lowestoft, UK}
\address[3]{Université Pierre et Marie Curie, 4 Place Jussieu, 75005 Paris,
	France}
\address[4]{Wageningen Marine Research, Haringkade 1 1976 CP IJmuiden,
	Netherlands}

\begin{abstract}
%\textcolor{gray}{[Guidance: A concise and factual abstract is required. The abstract 
%should state briefly the purpose of the research, the principal results and
%major conclusions. An abstract is often pnresented separately from the article,
%so it must be able to stand alone. For this reason, References should be
%avoided, but if essential, then citep the author(s) and year(s). Also,
%non-standard or uncommon abbreviations should be avoided, but if essential they
%must be defined at their first mention in the abstract itself.  Graphical
%abstract: Although a graphical abstract is optional, its use is encouraged as
%it draws more attention to the online article. The graphical abstract should
%summarize the contents of the article in a concise, pictorial form designed to
%capture the attention of a wide readership. Graphical abstracts should be
%submitted as a separate file in the online submission system. Image size:
%Please provide an image with a minimum of 531 X 1328 pixels (h X w) or
%proportionally more. The image should be readable at a size of 5 x 13 cm using
%a regular screen resolution of 96 dpi.  Preferred file types: TIFF, EPS, PDF or
%MS Office files.] \\}
%
Fishing exploits spatially and temporally hetergenous fish populations, using
species-unselective gear that can result in unintended, unwanted catch of low
quota or protected species. Reducing these unwanted catches is crucial for
biological and economic sustainability of `mixed fisheries' and implementation
of an ecosystem approach to fishing. \\

@@

%\textcolor{gray}{[Guidance:: State the objectives of the work and provide an 
%adequate background, avoiding a detailed literature survey or a summary of the
%results.] \\}
%
Fishers exploit fish populations that are heterogenously distributed in space
and time with verying knowledge of species distributions using
species-unselective fishing gear. Fisheries that catch an assemblage of
species, known as mixed fisheries, when managed by single-species quotas can
end up discarding overquota catch leading to overexploitation of fish
populations. Reducing discarding is crucial to ensure biological and economic
sustainability of fisheries and implementation of an ecosystem approach to
fisheries. As such there is increasing interest in technical solutions such as
gear and spatial closures as ways of avoiding discards.  \\

Use of spatial management as a tool has been proposed as a method to reduce
discards. However, its implementation is hampered by lack of knowledge of fish
and fishery spatiotemporal dynamics and understanding of the scale at which
processes are important for management. Understanding the correct scale for
spatial management is crucial in order to implement measures at a resolution
that ensures effective management \citep{Dunn2016} while minimising economic
impact. For example, a scale that promotes species avoidance for vulnerable or
low quota species while allowing continuance of sustainable fisheries for
available quota species. \\

Ensuring measures are implemented at an appropriate scale has been a challenge
in the past that has led to ineffectual measures with unitended consequences
such as limited impact towards the management objective or increased benthic
impact on previously unexploited areas (e.g. the cod closure in the North
Sea \citep{Rijnsdorp2001,Dinmore2003}). Since then more refined spatial
information has become available through the combination of logbook and Vessel
Monitoring System (VMS) data \citep{Lee2010, Bastardie2010, Gerritsen2012,
	Mateo2016} and more real-time spatial management has been possible 
	\citep[e.g.][]{Holmes2011}. Such information is, however, patchy and
derived from an inherently biased sampling programme (i.e. targeted fishing).
Further, fishers generally only recorded landings (not catch) on a daily basis.
This leads to questions about the validity of inference that can be drawn from
landings data assigned to VMS activity pings. \\

@@

We simulate a fishery closure to protect one species based on the
fishery-dependent inferred distributions at a spatial and temporal scale
typical in fisheries management, and assess a theoretical "benefit" to the
population, and effect on the other three populations. Further, we extend our
analysis to a range of spatial and temporal scales to assess the impact of
these processes on the success of the management measure. \\

@@

%\textcolor{gray}{[Guidance: Provide sufficient details to allow the work to be
%reproduced by an independent researcher. Methods that are already published
%should be summarized, and indicated by a reference.  If quoting directly from a
%previously published method, use quotation marks and also citep the source. Any
%modifications to existing methods should also be described.] \\ }
%
We develop a simulation model with a modular event-based approach, where
modules are implemented on independent time-scales appropriate to capture the
characteristic of the process modelled (Figure 1). The fishing model operated on a
tow-by-tow basis, while population dynamics (fishing and natural mortality,
growth) operate on a daily time-step.  Population movement occurs on a
weekly time-step, while recruitment occurs periodcally each year for a set
time period (e.g. 3 weeks) at at specified point individual to a species. The
simulation framework is implemented in the statistical software package R
\citep{RCoreTeam2017}; available as an R package from the authors github
(\url{www.github.com/pdolder/MixFishSim}).\\

Here we describe each of the model components; 1)
Population dynamics, 2) Recruitment dynamics, 3) Population movement, 4)
fishery dynamics.

@@

The basic population level processes are simulated using a modified two-stage
Deriso-Schnute delay difference model \citep{Deriso1980, Schnute1985,
	Dichmont2003} occurring at a daily time-step. Here, population biomass
growth and depletion for pre-recruits and fish recruited to the fishery are
modelled separately as a function of previous recruited biomass, intrinsic
population growth and recruitment:

\begin{equation*}
	\begin{split}
	B_{y,d+1} = &\\
	& (1 + \rho) B_{y,d} \cdot e^{-Z_{y,d}} - \rho \cdot e^{-Z_{y,d}} \hspace{2.9cm}
	\times \\  
	& (B_{y,d-1} \cdot e^{-Z_{y,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot R_{\tilde{y}(y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(y,d)} 
	\end{split}
\end{equation*}

where $\rho$ is Brody's coefficient, shown to be approximately equal to
$exp(-K)$, where $K$ is the growth rate from a von bertalanffy logistic growth
model \citep{Schnute1985}. $Wt_{R-1}$ is the weight of fish prior to
recruitment, while $Wt_{R}$ is the recruited weight. $\alpha_{d}$ represents
the proportion of fish recruited during that day for the year, while
$R_{\tilde{y}}$ is the annual recruits. \\

Mortality $Z$ can be decomposed to natural mortality, $M$, and fishing
mortality, $F$, where both $M$ and $F$ are instantaneous rates with $M$ fixed
and $F$ calculated by solving the Baranov catch equation \citep{Hilborn1992b}
for $F$:

\begin{equation*}
C_{d} = \frac{F_{d}}{F_{d}+M_{d}} * (1 - e^{-(F_{d} + M_{d})}) * B
\end{equation*}

where $C$ is the summed catch from the fishing model across all fleets and
vessels for the population during the day, and $B$ the daily biomass for the
species. \textcolor{red}{[link $F$ to effort and catchability - as I think we
	have F as an emergent property of the fleets rather than something we
	solve for (I could be wrong though!) - catch for a vessel is a product of
	catchability and biomass, i.e. C = qB, but this catch is summed to
	solve for F. So its both really]}\\

@@

\begin{equation*}
	\begin{split}
	\bar{R} = & \frac{(\alpha * B)}{(\beta + B)} \\
	     R \sim & \log N[(\log(\bar{R}),\log(\sigma^2))]
	\end{split}
\end{equation*}
Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum, $B$ current SSB and
$\sigma^2$ the variability in the recruitment due to stochastic
processes. \\

@@

\begin{equation*}
	\begin{split}
	\bar{R} = & B * e^{(\alpha - \beta * B)} \\	
   	     R \sim & \log N[(\log(\bar{R}),\log(\sigma^2))]
	\end{split}
\end{equation*}

@@

\subsection{Population movement}

@@

%\textcolor{gray}{[Guidance: If there is more than one appendix, they should 
%be identified as A, B, etc.  Formulae and equations in appendices should be
%given separate numbering: Eq.  (A.1), Eq. (A.2), etc.; in a subsequent
%appendix, Eq. (B.1) and so on.  Similarly for tables and figures: Table A.1;
%Fig. A.1, etc.]}
%
\begin{table}[!ht]
\caption{Population dynamics and movement parameter setting}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.15 & 1/0.05 & 1/0.55 & 1/0.05  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier & 10 & 10 & 10 & 10 \\
	Movement $\lambda$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit 'a' & 60 & 100 & 80 & 2 \\
	Beverton-Holt Recruit 'b' & 250 & 250 & 200 & 50 \\
	Beverton-Holt Recruit $\sigma^2$ & 0.4 & 0.3 & 0.4 & 0.3 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	$wt$ & 1 & 1 & 1 & 1 \\
	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
	M (annual) & 0.2 & 0.2 & 0.2 & 0.1 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}

>>>>

\usepackage{lineno,hyperref}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,chains,calc}
\usepackage{hhline}
\usepackage{booktabs}

% For track-changes
\usepackage[draft]{changes}
%\usepackage[final]{changes}
\definechangesauthor[color = red]{JM}
\definechangesauthor[color = blue]{PD}
\definechangesauthor[color = green!40!black]{JJ}
\definechangesauthor[color = purple]{CM}

@@

\address[1]{Galway-Mayo Institute of Technology (GMIT), Dublin Road, Galway,
	Ireland} 
\address[2]{Centre for Environment, Fisheries and Aquaculture Science (Cefas),
	Pakefield Road, Lowestoft, UK}
\address[3]{\replaced[id=JM]{Sorbonne Université, Faculty of
		Sciences}{Université Pierre et Marie Curie}, 4 Place Jussieu,
	75005 Paris, France}
\address[4]{Wageningen Marine Research, Haringkade 1 1976 CP IJmuiden,
	Netherlands}

\begin{abstract}
%\textcolor{gray}{[Guidance: A concise and factual abstract is required. The abstract 
%should state briefly the purpose of the research, the principal results and
%major conclusions. An abstract is often pnresented separately from the article,
%so it must be able to stand alone. For this reason, References should be
%avoided, but if essential, then citep the author(s) and year(s). Also,
%non-standard or uncommon abbreviations should be avoided, but if essential they
%must be defined at their first mention in the abstract itself.  Graphical
%abstract: Although a graphical abstract is optional, its use is encouraged as
%it draws more attention to the online article. The graphical abstract should
%summarize the contents of the article in a concise, pictorial form designed to
%capture the attention of a wide readership. Graphical abstracts should be
%submitted as a separate file in the online submission system. Image size:
%Please provide an image with a minimum of 531 X 1328 pixels (h X w) or
%proportionally more. The image should be readable at a size of 5 x 13 cm using
%a regular screen resolution of 96 dpi.  Preferred file types: TIFF, EPS, PDF or
%MS Office files.] \\}
%
\replaced[id = JJ]{Most fisheries}{Fishing} exploit\deleted[id=JJ]{s} spatially
and temporally hetergenous fish populations, using species-unselective gear
that can result in unintended, unwanted catch of low quota or protected
species. Reducing these unwanted catches is crucial for biological and economic
sustainability of `mixed fisheries' and implementation of an ecosystem approach
to fishing. \\

@@

%\textcolor{gray}{[Guidance:: State the objectives of the work and provide an 
%adequate background, avoiding a detailed literature survey or a summary of the
%results.] \\}
%
Fishers exploit fish populations that are heterogenously distributed in space
and time with verying knowledge of species distributions using
species-unselective fishing gear. Fisheries that catch an assemblage of
species, known as mixed fisheries \replaced[id=JJ]{may}{, when managed by
	single-species quotas can end up} discard\deleted[id=JJ]{ing} overquota
catch \added[id=JJ]{when managed by single species quotas,} leading to
overexploitation of fish populations \added[id=JJ]{\citep{Ulrich2011a,
		Batsleer2015}}.  \added[id=JJ]{This discarding of fish in
	excess of quota hampers the ability to limit fishing mortality to
	within sustainable limits \citep{Alverson1994, Crowder1998,
		Rijnsdorp2007}.} Reducing discarding is crucial to ensure
biological and economic sustainability of fisheries\deleted[id=JJ]{ and
	implementation of an ecosystem approach to
	fisheries}\replaced[id=PD]{and}{. As such} there is increasing interest
in technical solutions such as gear and spatial closures as ways of avoiding
discard\replaced[id=JJ]{ing of fish \citep{Kennelly2002, Catchpole2008,
		Bellido2011}}{s}.  \\

Use of spatial management as a tool has been proposed as a method to reduce
discards \added[id=PD]{\citep{Holmes2011, Little2014, Dunn2014a}}. However, its
implementation is hampered by lack of knowledge of fish and fishery
spatiotemporal dynamics and understanding of the scale at which processes are
important for management. Understanding the correct scale for spatial
management is crucial in order to implement measures at a resolution that
ensures effective management \citep{Dunn2016} while minimising economic impact.
For example, a scale that promotes species avoidance for vulnerable or low
quota species while allowing continuance of sustainable fisheries for available
quota species. \\

Ensuring measures are implemented at an appropriate scale has been a challenge
in the past that has led to ineffectual measures with unitended consequences
such as limited impact towards the management objective or increased benthic
impact on previously unexploited areas (e.g. the cod closure in the North
Sea \citep{Rijnsdorp2001,Dinmore2003}). Since then more refined spatial
information has become available through the combination of logbook and Vessel
Monitoring System (VMS) data \citep{Lee2010, Bastardie2010, Gerritsen2012,
	Mateo2016} and more real-time spatial management has been possible 
	\citep[e.g.][]{Holmes2011}. Such information is, however, patchy and
derived from an inherently biased sampling programme (i.e. targeted fishing).
Further, fishers generally only recorded landings (not catch) on a daily
basis\footnote{\added[id=JJ]{Its not clear what the problem is: landed
		collected on daily basis or landings recorded rather than catch}}.
This leads to questions about the validity of inference that can be drawn from
landings data assigned to VMS activity pings\footnote{\added[id=JJ]{This comes as a
	surprise: I thought this was going to be about discards}}. \\

@@

We simulate a fishery closure to protect one species based on the
fishery-dependent inferred distributions at a spatial and temporal scale
typical in fisheries management, and assess a theoretical "benefit" to the
population, and effect on the other three populations\footnote{\added[id=JJ]{If
		the paper has two goals this should be clear from the start,
		but may be better over 2 MSs}}. Further, we extend our analysis
to a range of spatial and temporal scales to assess the impact of these
processes on the success of the management measure. \\

@@

%\textcolor{gray}{[Guidance: Provide sufficient details to allow the work to be
%reproduced by an independent researcher. Methods that are already published
%should be summarized, and indicated by a reference.  If quoting directly from a
%previously published method, use quotation marks and also citep the source. Any
%modifications to existing methods should also be described.] \\ }
%
\replaced[id=PD]{A}{We developed and implemented a simulation model with a}
modular event-based \replaced{simulation model was developed with}{approach,
	where} \added[id=PD]{sub-}modules \deleted[id=PD]{are} implemented on
independent time-scales appropriate to capture the characteristic of the
\replaced[id=PD]{different processes}{process modelled} (Figure 1).
\added[id=PD]{The following sub-modules were included to capture the full
	system: 1) Population dynamics, 2) Recruitment dynamics, 3) Population
	movement, 4) fishery dynamics.} \\

\deleted[id=PD]{The fishing model operated on a tow-by-tow basis, while}
\replaced[id=PD]{P}{p}opulation dynamics (fishing and natural mortality,
growth) operate on a daily time-step\replaced[id=PD]{, while p}{. P}opulation
movement occurs on a weekly time-step\replaced[id=PD]{. R}{, while r}ecruitment
\replaced[id=PD]{takes place}{occurs} periodcally each year for a set time
\replaced[id=PD]{duration}{period (e.g. 3 weeks)} at at specified point
individual to a species\deleted[id=PD]{.}\added[id=PD]{, while the fishing
	module operates on a tow-by-tow basis (multiple events a day)}. The
simulation framework is implemented in the statistical software package R
\citep{RCoreTeam2017} \replaced[id=PD]{and}{;} available as an R package from
the authors github (\url{www.github.com/pdolder/MixFishSim}).\\

\deleted[id=PD]{Here we describe each of the model components; 1)
Population dynamics, 2) Recruitment dynamics, 3) Population movement dynamics, 4)
fishery dynamics.}

@@

The basic population level processes are simulated using a modified two-stage
Deriso-Schnute delay difference model \citep{Deriso1980, Schnute1985,
	Dichmont2003} occurring at a daily time-step. \added[id=PD]{A daily
	time-step was chosen as to discretise continuous population processes
	on a biologically relevent and computationally tractable timescale.}
\replaced[id=PD]{Under the popualation dynamics module}{Here,} population
biomass growth and depletion for pre-recruits and \deleted[id=PD]{fish}
recruited \added[id=PD]{fish} \deleted[id=PD]{to the fishery} are modelled
separately as a function of previous recruited biomass, intrinsic population
growth and recruitment:

\begin{equation*}
	\begin{split}
	B_{c,d+1} = &\\
	& (1 + \rho) B_{c,d} \cdot e^{-Z_{c,d}} - \rho \cdot e^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& (B_{c,d-1} \cdot e^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
	R_{\tilde{y}(c,y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
	\end{split}
\end{equation*}

where $\rho$ is Brody's coefficient, shown to be approximately equal to
$exp(-K)$, where $K$ is the growth rate from a von bertalanffy logistic growth
model \citep{Schnute1985}. $Wt_{R-1}$ is the weight of fish prior to
recruitment, while $Wt_{R}$ is the recruited weight. $\alpha_{d}$ represents
the proportion of fish recruited during that day for the year, while
$R_{\tilde{c,y}}$ is the annual recruits in cell $c$ for year $y$. \\

Mortality $Z_{c,d}$ can be decomposed to natural mortality, $M_{c,d}$, and
fishing mortality, $F_{c,d}$, where both $M_{c,d}$ and $F_{c,d}$ are
instantaneous rates with $M_{c,d}$ fixed and $F_{c,d}$ calculated by solving
the Baranov catch equation \citep{Hilborn1992b} for $F_{c,d}$:

\begin{equation*}
C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} * (1 - e^{-(F_{c,d} + M_{c,d})}) *
B_{c,d}
\end{equation*}

where $C_{c,d}$ is the summed catch from the fishing model across all fleets
and vessels in cell $c$ for the population during the day $d$, and $B_{c,d}$
the daily biomass for the population in the cell. \textcolor{red}{[link $F$ to
	effort and catchability - as I think we have F as an emergent property
	of the fleets rather than something we solve for (I could be wrong
	though!) - catch for a vessel is a product of catchability and biomass,
	i.e. C = qB, but this catch is summed to solve for F. So its both
	really]}\\

@@

\begin{equation*}
	\begin{split}
	\bar{R}_{c,d} = & \frac{(\alpha * B_{c,d})}{(\beta + B_{c,d})} \\
	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
	\end{split}
\end{equation*}
Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum, $B$ current SSB and
$\sigma^2$ the variability in the recruitment due to stochastic
processes. \\

@@

\begin{equation*}
	\begin{split}
	\bar{R}_{c,d} = & B_{c,d} * e^{(\alpha - \beta * B_{c,d})} \\	
   	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
	\end{split}
\end{equation*}

@@

\subsection{Population movement dynamics}

@@

%\textcolor{gray}{[Guidance: If there is more than one appendix, they should 
%be identified as A, B, etc.  Formulae and equations in appendices should be
%given separate numbering: Eq.  (A.1), Eq. (A.2), etc.; in a subsequent
%appendix, Eq. (B.1) and so on.  Similarly for tables and figures: Table A.1;
%Fig. A.1, etc.]}
%

\begin{table}[!ht]
	\centering
	\caption{Description of variables for sub-modules}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population dynamics}}  \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Delay-difference model}} \\
		\hline
		$B_{c,d}$ & Biomass in cell $c$ and day $d$ & kg \\
		$Z_{c,d}$ & Total mortality in cell $c$ for day $d$ & - \\
		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
		$\rho$ & Brody's growth coefficient & yr\textsuperscript{-1} \\
		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
		$Wt_{R-1}$ & Weight of a pre-recruit fish & kg \\
		$\alpha_{d}$ & Proportion of annually recruited fish recruited
		during day $d$ & - \\
		\hline
		\multicolumn{3}{l}{\textit{Baranov catch equation}} \\
		\hline
		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
		$F_{c,d}$ & Instantaneous rate of fishing mortality in cell $c$
		on day $d$ & - \\
		$M_{c,d}$ & Instantaneous rate of natural mortality in cell $c$
		on day $d$ & - \\
		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
		\hline
		\multicolumn{3}{c}{\textbf{Recruitment dynamics}} \\
		\hhline{===}
		$\tilde{R}_{c,d}$ & is the recruitment in cell $c$ for day $d$ & $d^{-1}$ \\
		$B_{c,d}$ & is the Biomass in cell $c$ for day $d$ & $d^{-1}$ \\
		$\alpha$ & the maximum recruitment rate & kg  \\
		$\beta$ & the biomass required to produce half the maximum rate
		of recruitment & kg \\
		\hline
		\multicolumn{3}{c}{\textbf{Population movement dynamics}} \\
		\hhline{===}
		a & b & c \\
		a & b & c \\
		\hline
		\multicolumn{3}{c}{\textbf{Fleet dynamics}} \\
		\hhline{===}
		a & b & c \\
		a & b & c \\
		\bottomrule
	\end{tabular}
\end{table}

\begin{table}[!ht]
\caption{Population dynamics and movement parameter setting}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.15 & 1/0.05 & 1/0.55 & 1/0.05  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier & 10 & 10 & 10 & 10 \\
	Movement $\lambda$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit 'a' & 60 & 100 & 80 & 2 \\
	Beverton-Holt Recruit 'b' & 250 & 250 & 200 & 50 \\
	Beverton-Holt Recruit $\sigma^2$ & 0.4 & 0.3 & 0.4 & 0.3 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	$wt$ & 1 & 1 & 1 & 1 \\
	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
	M (annual) & 0.2 & 0.2 & 0.2 & 0.1 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}
